Timely Object Recognition

### 2012-12-01 writeups/nips12/poster/poster.tex
baller version

@@

        % Three parboxes allow for images on both sides of the title
        % box with the title text in the middle.
        \parbox{10cm} {
        \includegraphics[height=9cm]{../../figures/berkeley_seal.pdf}
        }
        \parbox{\arabic{title-box-width}cm} {
          \centering
              {\Huge \bf{Timely Object Recognition} } \\
              \vspace{1cm}
              \begin{tabular}{cccc}
                {\huge Sergey Karayev$^1$, \hfill} & {\huge Tobias Baumgartner$^2$, \hfill} & {\huge Mario Fritz$^3$, \hfill} & {\huge Trevor Darrell$^1$}\\\\
                \multicolumn{4}{c}{\Large $^1$UC Berkeley, \hspace{2cm} $^2$RWTH Aachen, \hspace{2cm} $^3$MPI Informatics}
              \end{tabular}
        }
        \parbox{10cm} {
          \includegraphics[width=10cm]{../../figures/MPI_logo.png}
        }

@@

    % ==============================================================================
    % ABSTRACT
    \path (title.south west) ++(0cm,-2cm) + (-\arabic{title-left-margin}cm,0cm) node(introduction) [style=tbox,text width=30cm] {
    \begin{itemize}
      \item Our task is multi-class object detection in a setting where there is not enough time to evaluate all detectors.

      \item We use reinforcement learning to learn a \emph{dynamic} policy for selecting detectors and classifiers, and learn to take actions that do not provide immediate reward.

      \item We evaluate detection performance vs. time with the novel \emph{timeliness} measure, and test on the PASCAL VOC challenge.
    \end{itemize}

    }; \addcenteredtitle{introduction}{Abstract} 
    % The above line adds the title ``Introduction'' to the box named ``introduction''.

    % ==============================================================================
    % FIGURE 1 WITH EXPLANATION 
    \path (introduction.south west) ++(0cm,-2cm) node(coding) [style=tbox,text width=30cm] {
      \begin{center}
        \includegraphics[width=24cm]{../../figures/pomdp_annotated.pdf}
      \end{center}

      \begin{itemize}
        \item An action $a \in \mathcal{A}$ can run detection for an object class $k$ in the whole image, or classify the scene.
        \item Potential actions are considered according to their predicted \emph{value} $Q(s,a)$, which also depends on the \emph{belief state} $s$ of the system.
        \item The selected action returns observations in the form of a list of detections, or simply an evaluated feature.
        \item Observations update the belief state through an inference process.
        \item The final evaluation is the area of the AP vs. Time curve between the start time $T_s$ and end time $T_d$.
      \end{itemize}

      \begin{center}\line(1,0){350}\end{center}

@@

    }; \addcenteredtitle{coding}{Sequential Detection}

    % ==============================================================================
    % Learning the Policy 
    \path (introduction.north east) ++(2cm,0cm) node(model) [style=tbox,text width=34 cm] {
      \begin{center}
        \includegraphics[width=30cm]{../../figures/figure1_extended_hor.pdf}
      \end{center}

      We define our policy as taking an untaken action with maximum value.
      \begin{align*} \pi(s) = \arg\max_{a_i \in \mathcal{A} \setminus \mathcal{O}} Q(s,a_i) = \theta_\pi^\top \phi(s,a) \end{align*}

      The value function
      \begin{align*}Q^\pi(s^j,a) = \mathbb{E} [R \mid s, a, \pi)]\end{align*}
      where $R = \sum_{i=j}^J \gamma^{i-j} R(s^i,a^i)$ and $J$ is the index of the last action before deadline time $T_d$.

      \parbox{20cm}{
      \textbf{Reward Function:} The final performance evaluation of area under the AP vs. Time curve between $T_s$ and $T_d$ is additive per action.
      We define the reward function as
      \begin{align*} R(s^j,a) = \Delta \text{ap} (t_T^j-\frac{1}{2}\Delta t) \end{align*}}
      \parbox{14cm}{
      \begin{center}
        \includegraphics[height=10cm]{../../figures/apvst_expl.pdf}
      \end{center}}
      \\

      \begin{center}\textbf{Reinforcement Learning}\end{center}
      To compute , we run Monte Carlo policy iteration.
      We evaluate full episodes of the detection task on several thousand images, with a decreasing $\epsilon$-greedy policy.
      Policy weights $\theta$ are updated with $L_2$ regularization.

      \paragraph{}
      We evaluate different values of the reward discount $\gamma$, which at $0$ induces a completely greedy policy, and at $1$ has full lookahead.
      We find $\gamma = 0.4$ to work best in cross-validation.
      \\

    }; \addcenteredtitle{model}{Learning to Detect on a Budget}

    % ==============================================================================
    % RESULTS
    \path (model.north east) ++(2cm,0cm) node(results) [style=tbox,text width=30cm] {
    We evaluated on the PASCAL VOC 2007 detection task, with 20 Deformable Part Model detectors (one per class), and an additional
    scene context action (GIST feature).
    \\

    \begin{center}\textbf{Feature Representation}\end{center}
      The features $\phi(s, a)$ are composed of\\

      {\small
      \begin{tabularx}{0.8\linewidth}{p{0.23\linewidth}p{0.69\linewidth}}
      $P(C_a)$ & The prior probability of presence of the class that corresponds to the detector of action $a$ (omitted for the scene-context action).\\

      $P(C_0|\mathbf{o}) \ldots P(C_K|\mathbf{o})$ & The presence probabilities for all classes, conditioned on the current set of observations.\\

      $H(C_0|\mathbf{o}) \ldots H(C_K|\mathbf{o})$ & The entropies for all classes, conditioned on the current set of observations. \\

      $t^j_T$ & The time until deadline, and four other time features.\\
      \end{tabularx}
      }\\\\

      \begin{center}\textbf{Updating the belief state}\end{center}
      Observations $\mathbf{o}$ of detector for class $k$ update $P(C_k|\mathbf{o})$ either \emph{directly} (using a probability estimated by a classifier trained on the detector output) or through an \emph{MRF}.
      The MRF is learned with $L_1$-regularization and inference is done with loopy belief propagation.

    \parbox{12cm}{
    \textbf{Weights} Learning with a higher $\gamma$ results in policies more relient on the global scene feature, for example.}%
    \parbox{18cm}{\hfill
    \includegraphics[width=17cm]{../../figures/weights.pdf}}
    \\\\

@@

    \begin{center}
    \begin{tabular}{|c|c|c|c|c|c|}
    \hline
    Bounds & Random & Fixed Order & RL        & RL w/ GIST         & Oracle \\ \hline
    (0,20) & 0.250  & 0.342       & 0.378     & \textbf{0.382}  & 0.488 \\ 
    (0,10) & 0.119  & 0.240       & 0.266     & \textbf{0.267}  & 0.464 \\ 
    (5,15) & 0.257  & 0.362       & 0.418     & \textbf{0.420}  & 0.530 \\ \hline
    \end{tabular}
    \end{center}

    }; \addcenteredtitle{results}{Results}

\end{tikzpicture}

\end{center}
\end{document}

>>>>

\newcommand{\argmax}[1]{\underset{#1}{\operatorname{arg}\operatorname{max}}\;}

@@

        % Three parboxes allow for images on both sides of the title
        % box with the title text in the middle.
        \parbox{10cm} {
        \includegraphics[height=8cm]{../../figures/berkeley_seal.pdf}
        }
        \parbox{\arabic{title-box-width}cm} {
          \centering
              {\Huge \bf{Timely Object Recognition} } \\
              \vspace{1cm}
              \begin{tabular}{cccc}
                {\Large Sergey Karayev$^1$, \hfill} & {\Large Tobias Baumgartner$^2$, \hfill} & {\Large Mario Fritz$^3$, \hfill} & {\Large Trevor Darrell$^1$}\\\\
                \multicolumn{4}{c}{\large $^1$UC Berkeley, \hspace{2cm} $^2$RWTH Aachen, \hspace{2cm} $^3$MPI Informatics}
              \end{tabular}
        }
        \parbox{10cm} {
          \includegraphics[width=10cm]{../../figures/MPI_logo.png}
        }

@@

    %%% MOTIVATION
    \path (title.south west) ++(0cm,-2cm) + (-\arabic{title-left-margin}cm,0cm) node(motivation) [style=tbox,text width=28cm] {
    \textbf{\textsc{Problem}}
    \begin{itemize}
      \item Want to detect objects of many classes in an image.
      \item Detectors and classifiers already exist, but there is \textbf{not enough time to run all detectors}.
    \end{itemize}

    \textbf{\textsc{Approach}}
    \begin{itemize}
      \item Formulate \textbf{timeliness} evaluation of detection performance vs. time.
      \item Treat detectors and classifiers as ``black boxes''; use reinforcement learning to find a \textbf{dynamic} policy for deploying them.
    \end{itemize}

    \textbf{\textsc{Results}}
    \begin{itemize}
      \item Learn to take actions that do not provide immediate reward.
      \item Wrapping per-class detectors in our system and setting a deadline\\\textbf{increases the multi-class Average Precision at deadline and before.}
    \end{itemize}
    }; \addcenteredtitle{motivation}{1. Motivation}

    %%% MODEL & REINFORCEMENT LEARNING
    \path (motivation.south west) ++(0cm,-2cm) node(implementation) [style=tbox,text width=28cm] {
      \parbox{16cm}{
      \textbf{\textsc{AP vs Time and the Reward}}
      \begin{itemize}
        \item The final performance evaluation is the area under the AP vs. Time curve between $T_s$ and $T_d$.
        \item Because this is additive per action, we define \begin{align*} R(s^j,a) = \Delta \text{ap} (t_T^j-\frac{1}{2}\Delta t) \end{align*}
      \end{itemize}
      }
      \parbox{12cm}{\hfill\includegraphics[width=11cm]{../../figures/apvst_expl.pdf}}
      \\

      \textbf{\textsc{Learning $\pi(s)$}} with fitted Q-iteration iteration.
      \begin{itemize}
        \item Gather samples under current $\pi$ by running detection episodes on several thousand images.
        \item Update policy-defining weights $\theta$ with $L_1$ regularization
        \item Gradually decrease $\epsilon$-greediness of policy.
      \end{itemize}
      \vspace{1cm}

      \textbf{\textsc{Reward discount $\gamma$}}
      \begin{itemize}
      \item $\gamma=0$ induces a completely greedy policy, and at $\gamma=1$ is full lookahead.
      \item $\gamma = 0.4$ performs best in cross-validation on the final evaluation.
      \end{itemize}
      \vspace{1cm}

      \textbf{\textsc{The belief state}} posterior $P(C_k|\mathbf{o})$ is updated with observations $\mathbf{o}$ of detector for class $k$.
      \begin{itemize}
        \item \emph{Direct} method simply replaces the posterior of the corresponding class(es).
        \item \emph{MRF} (pictured) method runs loopy BP in an MRF model, updating all posteriors.
        \item MRF weights are learned with $L_1$-regularization.
      \end{itemize}
    }; \addcenteredtitle{implementation}{3. Implementation}

    %%% FIGURE 1
    \path (motivation.north east) ++(2cm,0cm) node(figure1) [style=tbox,text width=38cm] {
      \begin{center}
        \includegraphics[width=38cm]{../../figures/figure1_with_pomdp.pdf}
      \end{center}
      \begin{itemize}
        \item Action $a \in \mathcal{A}$ can run detector of object class $k$ on whole image, or classify the scene.
        \item The selected action returns observations $\mathbf{o}$: a list of detections, or an evaluated feature.
        \item We define our policy as taking an untaken action with maximum value. \begin{align*} \pi(s) = \argmax{a_i \in \mathcal{A} \setminus \mathcal{O}} Q(s,a_i) = \theta_\pi^\top \phi(s,a) \end{align*}
        \item Must learn an accurate approximation of the value function \begin{align*}Q^\pi(s^j,a) = \mathbb{E} [R \mid s, a, \pi)]\end{align*} where $R = \sum_{i=j}^J \gamma^{i-j} R(s^i,a^i)$ and $J$ is the index of the last action before deadline time $T_d$.
      \end{itemize}
    }; \addcenteredtitle{figure1}{2. Sequential Multi-class Detection}

%%% FEATURES AND WEIGHTS
    \path (figure1.south west) ++(0cm,-2cm) node(features) [style=tbox,text width=38cm] {
      The features $\phi(s, a)$ reflect
      \begin{itemize}
        \item the probability that class $C$ is present in the image and its degree of certainty, for all classes.
        \item time to $T_s$ and to $T_d$, and the expected time of the action.
      \end{itemize}
      \vspace{5mm}

      \parbox{18cm}{\includegraphics[width=17cm]{../../figures/weights_greedy.pdf}\\\centering \small{\textbf{Greedy}}}\hfill%
      \parbox{18cm}{\includegraphics[width=17cm]{../../figures/weights_rl.pdf}\\\centering \small{\textbf{Reinforcement Learning}}}\\
      \begin{center}Learning with a higher $\gamma$ results in policies reliant on the global scene feature.\end{center}
    }; \addcenteredtitle{features}{4. Feature Representation and Policy Weights}

%%% RESULTS
    \path (figure1.north east) ++(2cm,0cm) node(results) [style=tbox,text width=28cm] {
      We evaluated on the PASCAL VOC 2007 detection task, with 20 Deformable Part Model detectors (one per class), and an additional
      scene context action (GIST feature).
      \\

@@

@@

      \begin{center}
      \begin{tabular}{|c|c|c|c|c|c|}
      \hline
      Bounds & Random & Fixed Order & RL        & RL w/ GIST         & Oracle \\ \hline
      (0,20) & 0.250  & 0.342       & 0.378     & \textbf{0.382}  & 0.488 \\ 
      (0,10) & 0.119  & 0.240       & 0.266     & \textbf{0.267}  & 0.464 \\ 
      (5,15) & 0.257  & 0.362       & 0.418     & \textbf{0.420}  & 0.530 \\ \hline
      \end{tabular}
      \end{center}
    }; \addcenteredtitle{results}{5. Evaluation}

%%% Conclusion
    \path (results.south west) ++(0cm,-2cm) node(conclusion) [style=tbox,text width=28cm] {
      Conclusions drawn, future work.
    }; \addcenteredtitle{conclusion}{6. Conclusion}

\end{tikzpicture}
\end{center}
\end{document}
